---
title: "Canada Forest Fires Statistics"
output: html_document
date: "2023-08-01"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk("./src/load_libraries.R")
knitr::read_chunk("./src/prepare_images.R")
knitr::read_chunk("./src/page_home.R")
knitr::read_chunk("./src/page_fire_counts.R")
knitr::read_chunk("./src/page_burned_area.R")
knitr::read_chunk("./src/page_property_losses.R")
knitr::read_chunk("./src/ui_elements.R")
knitr::read_chunk("./src/server_logic.R")
```

# This chunk will run the code from the "load_libraries" chunk in load_libraries.R
```{r load_libraries_chunk}
source("./src/load_libraries.R")
```

# This chunk will run the code from the "prepare_images" chunk in prepare_images.R
```{r}
source("./src/prepare_images.R")
```


# This chunk will run the code from the "page_home" chunk in page_home.R
```{r}
source("./src/page_home.R")
```


# This chunk will run the code from the "page_fire_counts" chunk in page_fire_counts.R
```{r}
source("./src/page_fire_counts.R")
```


# This chunk will run the code from the "page_burned_area" chunk in page_burned_area.R
```{r}
source("./src/page_burned_area.R")
```


# This chunk will run the code from the "page_property_losses" chunk in page_property_losses.R
```{r}
source("./src/page_property_losses.R")
```

# This chunk will run the code from the "ui_elements" chunk in ui_elements.R
```{r}
source("./src/ui_elements.R")
```

# This chunk will run the code from the "server_logic" chunk in server_logic.R
```{r}
source("./src/server_logic.R")
```

# Run the app
```{r}
shinyApp(ui = ui, server = server)
```